How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-26 docs/PhysicsPaper/StokesErosion.tex
noted where I left off
NM

@@

%-------------------------------------------------------------------%
\subsection{Transverse permeability and anisotropy}

@@

As given in \eqref{eq:anis}, the ratio of longitudinal to transverse permeability defines the anisotropy of the medium, $\anis = k_{11} / k_{22}$.

>>>>

\todo[inline]{Bryan left off here}

@@

%-------------------------------------------------------------------%
\subsection{Transverse permeability and anisotropy}
\label{subsec:anis}

@@

As given in \eqref{eq:anis}, the ratio of longitudinal to transverse permeability defines the anisotropy of the medium, $\anis = k_{11} / k_{22}$, which is plotted in Fig.~\ref{fig3}(b) over the course fo the simulation (solid curve). Early in the simulation the anisotropy is nearly one, as the initial configuration of randomly placed circles has no preferred flow direction. The anisotropy then increases as heterogeneous rates of erosion promote longitudinal flow over transverse flow. The anisotropy peaks at a value of $\anis \approx 4$ later in the simulation. At very late times, the anisotropy approaches unity again as the bodies completely vanish and return the system to a state of no preferred flow direction.

As discussed in Section \ref{subsec:anis}, the anisotropy of the medium results from the combination of {\em shape} anisotropy, at the individual grain level, and {\em configurational anisotropy}, at the large-scale level. As detailed in Section \ref{subsec:anis}, the configurational anisotropy can be extracted by replacing any
